|

### 2024-10-30 docs/paper.qmd
SSRN paper version

---
title: |
  | How does the Accounting Research Community
  | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management. We thank Kris Hardies as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, and WHU for providing helpful feedback. Scott Summers and David Wood thankfully provided data from the BYU Accounting Research Rankings. Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

@@

Cumulative science builds on the reproducibility of research, which is the ability to recreate the results of prior studies using the same materials as were used by the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods. Open science implies conducting research in ways that allow others to collaborate and contribute. Two central open science methods that have been put forward as strategies to improve the reproducibility of our work are the public sharing of research materials and the pre-registration of study plans. Over the last years, there has been a significant uptake of these open sciences methods in social science areas outside of accounting [@FLCPSWMBP_2023].

@@

Based on the responses of `r nrow(sd)` published accounting researchers, we find that attitudes towards open science clearly differ from those of other social science researchers. Most prominently, accounting researchers tend to hold a generally more pessimistic view of the reproducibility of influential work within their field. Compared to economists and sociologists, for example, accounting researchers are about half a point more skeptical on a 5-point Likert scale. Exploring this assessment across the respondents' demographics, we find this skepticism to be relatively stable. Analytical and qualitative researchers are somewhat more pessimistic. Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.

Given this finding, one would expect accounting researchers to take a proactive stance and embrace two prominent open science methods that are expected to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans. Turning first to the public sharing of research materials, we document that, again compared to researchers from other social science areas, accounting researchers are somewhat less familiar with this activity and assess it to be somewhat less important. Familiarity is largest for respondents using archival, field, and experimental methods and lowest for respondents using qualitative methods, who also perceive the sharing of research materials as less important.

Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in accounting researchers' perceived (prescriptive) importance of research material sharing, their stated willingness to share research materials, and their (descriptive) perception about actual sharing behavior in the accounting research community. 57% of our respondents state that they, at least sometimes, publicly share their research materials. In addition, our respondents believe that about 44% of them favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials. Although this sounds comforting and consistent with a general supportive stance of the accounting community toward research material sharing, the percentage comes down to a much more sobering 28% when respondents are asked about actual sharing behavior in the accounting research community. This assessment and the gap it reveals differ significantly across methodological areas. Analytical researchers have the most narrow gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials). Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share). The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).

@@

To contrast these perceptions from our survey with actual behavior, we gather additional observational data from a country-stratified random sample of `r nrow(authors)` authors of our target population. We find evidence for at least some form of research material sharing for 39% of the authors in this sample. This number is similar to the self-reported perception of actual research material sharing in our survey (i.e., 38%). However, when we inspect the observational data further, we find that research material sharing in accounting is largely an occasional compliance activity. For instance for 7.5% of the papers written by the authors in the observational data show evidence for research material sharing. Also, when we exclude Journal of Accounting Research and Management Science, two journals with data and code sharing policies, the share of authors for which we document at least some form of research material sharing drops from 39% to 23%. Furthermore, we document very few pre-registrations in our observational data, and all are linked to the Registered Report Initiative of the Journal of Accounting Research.

In light of these numbers, a logical next step is to explore the main rationales for and against sharing research materials. We do so based on a short experimental design using a hypothetical scenario and by using our survey data.[^2] In our hypothetical scenario involving a fellow researcher requesting access to participants' research materials, our participants state that they would be very likely to share on average (mean probability is 72%). We find no evidence that this probability is affected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope of the sharing decision (public versus private sharing). Based on the verbal response of our participants, researchers tend to share their materials as they believe that this improves the quality of their research and of research in general. Also, they share because they want to support their fellow researchers. The most commonly stated reasons for not sharing research materials are the proprietary nature of the data used (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%). The reasons differ across methods. For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).

Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it. This is consistent with these tools currently being less established in the accounting domain than in other fields. The challenges that hinder reproducibility and the potential effectiveness of open science methods vary across methodological paradigms. Qualitative research faces different challenges than archival quantitative work, and they both differ again from experimental studies. We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.

@@

Accounting is a field within the social sciences. As such, many of the arguments that have been developed with regard to the costs and benefits of open science in general [@AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023] also apply to the field of accounting. In the following, we present and extend some of these thoughts in a voluntary disclosure framework [@BCLW_2010]. For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration. Understood as a disclosure activity related to underlying research, publicly available research materials constitute a public good. To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and very likely also the quality of research. Even if they are not really reusable or reusing them would be prohibitively costly, they still reduce the costs of reproducing the original work, thereby reducing assurance costs. As the work in auditing [e.g., @S_1980] posits, reduced auditing costs (easier reproduction) should lead to an overall increase in audit quality (more and better reproductions) resulting in better financial reporting quality (better research).

This means that similar to other disclosure activities, sharing research materials does not necessarily benefit the producer but the research community at large. While intrinsic motivation for good research can be expected to be a strong determinant for individuals self-selecting into the academic accounting profession, one can still expect accounting researchers to under-engage in research material sharing because the production costs are mostly private while the benefits are mostly public. So, are there any private benefits of research material sharing? Besides the warm glow of helping others, research material sharing likely improves the quality of the sharing individual's research output. First, it increases the likelihood that mistakes, conditionally on being present, are being detected. As it seems safe to assume that such incidents impose a cost on sharing researchers, this should increase their incentives to increase research quality prior to sharing. Second, if research materials are shared relatively early, the sharing researcher can directly benefit from community feedback prior to the ultimate publication of the study. Finally, uncovered mistakes are an important learning opportunity, likely improving research quality in the long run.

Based on these arguments, there are reasons to believe that voluntary research material sharing can act as a signal for research quality, creating an incentive for researchers to use it to signal the quality of their work in the publishing and career process. In ideal circumstances, we should obtain the well-known unraveling result where researchers even share and improve low-quality research because the research community would otherwise assume the worst [@M_1981]. One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the contemporary disclosure literature. Thus, for research materials sharing to be viable it is important that the costs of sharing are sufficiently low, especially for researchers that produce high quality work. Thus, it critically hinges on the above quality assurance process. Also, it depends on the direct and indirect costs of research material sharing to be bearable and to be at least comparable for high and low quality researchers.

The direct costs of research material sharing can be sizable. Preparing data, code and research procedures for dissemination requires time. While this time can be expected to also have a quality improvement effect (see above), at least some of the documentation work and code refactoring to increase accessibility and reusability creates costs that will not directly pay off on the quality of the underlying work. Another important factor to consider is the cost of maintaining publicly available materials. While some replication packages or similar materials are static in nature and require only limited maintenance, data and code packages can require ongoing updating and support activities. One important aspect of maintenance costs is that they increase significantly with public demand. As demand is directly linked to the scientific impact of the underlying work it can be argued that high maintenance cost sharing activities are likely to also be high benefit activities.

@@

Rational researchers can be expected to voluntarily share research materials when their private benefits outweigh their private costs. Whether this happens will critically depend on whether the signaling mechanism outlined above unfolds. In a credence good market like research, signaling is a key mechanism to avoid market failure. Based on the discussion above, a critical aspect could be the proprietary cost of competition as one could argue that this cost is higher for high quality researchers with innovative ideas than for low quality researchers that will likely face limited demand for their materials. Also the risks of reputation costs or misuse of materials could be higher for high quality researchers. On the other hand, it can be argued that direct costs should be lower for high quality researchers because of superior skills. Finally, outside options should be generally higher for high quality researchers meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their materials private.

The discussion should sound somewhat familiar to those that study voluntary disclosures by firms. What is different from our traditional firm-setting is that most researchers are not acting as entrepreneurs. Instead, they are employed by academic institutions or act as civil servants. This can to some extend mute the relevance of the benefits and the costs outlined above, at least for those researchers that hold tenured positions. In addition, the employing institutions might also interact with the decision whether or not to make research materials available. They are designing performance and tenure evaluation criteria that incentivize researchers. Also, they compensate researchers for their time and they provide them with infrastructure that influences and at times drastically reduces the direct costs of research material sharing. They might even hold property rights on the intellectual capital that their employees generate. Based on the public announcements of many leading academic institutions, it seems as if these are generally advocating the positive externalities of research material sharing. However, the incentive systems designed by these institutions appear at least in parts inconsistent with these announcements, as they are valuing individual research achievements in form of publications and only rarely publicly available research materials.

Finally, publishers and journals are influential for research material sharing decisions as well. Leading journals have established demanding data and code sharing guidelines, essentially transforming the voluntary disclosure decision to a mandatory disclosure requirement. While journals also compete for the best papers and it is an interesting question how this competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.

@@

After eliciting respondents' perceptions on reproducibility, a set of questions explores their familiarity and experience with the practice of pre-registration. Lastly, we ask them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research. The survey ends with a few demographic questions. For a complete overview of the survey questions included in our study, please see Appendix A. All answers can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard} and the data itself are available in our public \href{https://github.com/joachim-gassen/osacc/}{GitHub repository} .

@@

Table 2 displays response demographics and characteristics based on a sample of up to 229 observations. Panel A reveals that the majority of the respondents is male, 35 years or older (87.8%), specializing in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%). Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we can collect about our population, we can only directly compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance. However, it seems likely that the study's all-European author team might have positively influenced the European response. While we control for geographical effects in our response (not-tabulated but available using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.

@@

The first research question of our study is to explore how accounting researchers perceive the reproducibility of influential findings in their field. Table 3 provides a comprehensive overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers with those of researchers in other disciplines as recorded by @FLCPSWMBP_2023, based on their question, "How confident are you that the influential research findings in \[discipline\] would replicate?" Notably, we adapted the wording in this question from "replicate" to "reproduce" to ensure clarity for our audience, recognizing the nuanced distinctions between these terms across various research methodologies. The term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000]. It implies the ability to recreate the results of prior studies using the same materials, procedures, and data as were used by the original researchers [@NSF_2015]. In contrast, the term "replication" has different interpretations for different fields. For instance, for experimental researchers, it refers to a distinct activity than reproduction (i.e., repeating an experimental study with new participants), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same or similar data using the same procedures). In turn, the definition that @FLCPSWMBP_2023 use for replication ("test of whether new studies on the same topic in a broadly similar sample support the same results.") seems relatively close to what we believe the common understanding of reproduction is in the area of accounting is. If anything, our notion of reproduction seems less demanding than the replication definition by @FLCPSWMBP_2023.

@@

The results in Table 3 reveal that accounting researchers generally hold a more critical view of the reproducibility of our influential findings. Compared to their peers in economics and sociology, accounting researchers exhibit a greater degree of doubt about the reproducibility of their influential work, with a difference of about half a point on a 5-point Likert scale. This difference is less stark when we compare accounting researchers to researchers in the fields of Political Science and Psychology. In a field fixed effect regression, in which we use Accounting as the baseline, we find that all four fixed field effects are statistically different from zero (two-tailed p-value \< 0.01). This skepticism is consistent with us accountants being more concerned about research quality hinting at the existence of a credence-good problem that open science methods are designed to address.

@@

To delve deeper, we examine the assessments of reproducibility across different methodologies within Accounting. Accounting is not only a diverse discipline in terms of orientation and topic but also in terms of the methodologies its researchers employ. We distinguish among five categories: Analytical, Archival/Field, Experimental, Qualitative, and Survey. We asked respondents which of those categories best described their main methodological area, enabling us to categorize them in the data. Table 4 presents their assessments regarding the reproducibility of influential findings across three panels. Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.

@@

Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field relative to neighboring fields. Given this skepticism and following our discussion in section 2, one might expect accounting researchers to take a proactive stance on open science approaches, particularly regarding the sharing of research materials. Following the old proverb by Supreme Court Justice Luis Brandeis "sunlight is the best disinfectant" one would expect accountants to support increased transparency in research. The survey assesses this argument by asking respondents two questions about the practice of sharing research materials, which we define as the practice of sharing data, code, and research procedures. These two questions are also close adaptions of the survey done by @FLCPSWMBP_2023.

@@

To visualize the differences between these three questions, Figure 5 displays scatter box plots, one for each question and separately for each methodology. First, examining the three plots for the sample as a whole, the clear visual pattern emerges that the assessments of actual sharing behavior among accounting researchers lag behind assessments of whether accounting researchers favor sharing, which, in turn, lags behind assessment of whether editors value sharing. This pattern seems starker for respondents in the Archival/Field category. These findings suggest a contrast between the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior. In other words: We believe that we should share and we also state that we do but we do not believe that others do.

@@

Our survey has so far revealed that accounting researchers who participated in our survey are more skeptical about reproducibility than other social science areas. We also find that they are less familiar with research materials sharing as an open science practice that helps address reproducibility and that they find that practice less important. Besides research material sharing, our survey also covers a second Open Science practice: Pre-registration.

@@

Table 8 summarizes three questions about pre-registration. Panel A considers respondents' familiarity with the practice itself. We asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^6] The results in Panel A suggest accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology. They seem to be slightly more familiar than researchers in Economics and Sociology (two-tailed p-value \< 0.010). While this finding might appear surprising at first glance, one has to factor in that the practice of pre-registration is gaining traction over time, and our survey was fielded two years later than the second wave of our benchmark survey.

>>>>

---
title: |
  | How does the Accounting Research Community
  | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management. We thank Kris Hardies, Maximilian Müller as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, and WHU for providing helpful feedback. Scott Summers and David Wood thankfully provided data from the BYU Accounting Research Rankings. Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

@@

Cumulative science builds on the reproducibility of research, which is the ability to recreate the results of prior studies using the same materials as those used by the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2020; @G_2023; @S_2023; @CGL_2024], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods. Open science implies conducting research in ways that allow others to collaborate and contribute. Two central open science methods that have been put forward as strategies to improve the reproducibility of our work are the public sharing of research materials and the pre-registration of study plans. Over the last years, there has been a significant uptake of these open sciences methods in social science areas outside of accounting [@FLCPSWMBP_2023].

@@

Based on the responses of `r nrow(sd)` published accounting researchers, we find that attitudes toward open science clearly differ from those of other social science researchers. Most prominently, accounting researchers tend to hold a generally more pessimistic view of the reproducibility of influential work within their field. Compared to economists and sociologists, for example, accounting researchers are about half a point more skeptical on a 5-point Likert scale. Exploring this assessment across the respondents' demographics, we find this skepticism to be relatively stable. Analytical and qualitative researchers are somewhat more pessimistic. Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.

Given this finding, one would expect accounting researchers to take a proactive stance and embrace two prominent open science methods that are expected to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans. Turning first to the public sharing of research materials, we document that, again, compared to researchers from other social science areas, accounting researchers are somewhat less familiar with this activity and assess it to be somewhat less important. Familiarity is largest for respondents using archival, field, and experimental methods and lowest for respondents using qualitative methods, who also perceive the sharing of research materials as less important.

Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in accounting researchers' perceived (prescriptive) importance of research material sharing, their stated willingness to share research materials, and their (descriptive) perception about actual sharing behavior in the accounting research community. 57% of our respondents state that they, at least sometimes, publicly share their research materials. In addition, our respondents believe that about 44% of them favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials. Although this sounds comforting and consistent with a generally supportive stance of the accounting community toward research material sharing, the percentage comes down to a much more sobering 28% when respondents are asked about actual sharing behavior in the accounting research community. This assessment and the gap it reveals differ significantly across methodological areas. Analytical researchers have the most narrow gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials). Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share). The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).

@@

To contrast these perceptions from our survey with actual behavior, we gather additional observational data from a country-stratified random sample of `r nrow(authors)` authors of our target population. We find evidence for at least some form of research material sharing for 39% of the authors in this sample. This number is similar to the self-reported perception of actual research material sharing in our survey (i.e., 38%). However, when we further inspect the observational data, we find that research material sharing in accounting is largely an occasional compliance activity. For instance, for 7.5% of the papers written by the authors in the observational data show evidence for research material sharing. Also, when we exclude Journal of Accounting Research and Management Science, two journals with data and code sharing policies, the share of authors for which we document at least some form of research material sharing drops from 39% to 23%. Furthermore, we document very few pre-registrations in our observational data, and all are linked to the Registered Report Initiative of the Journal of Accounting Research.

In light of these numbers, a logical next step is to explore the main rationales for and against sharing research materials. We do so based on a short experimental design using a hypothetical scenario and by using our survey data.[^2] In our hypothetical scenario involving a fellow researcher requesting access to participants' research materials, our participants state that they would be very likely to share on average (mean probability is 72%). We find no evidence that this probability is affected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope of the sharing decision (public versus private sharing). Based on the verbal responses of our participants, researchers tend to share their materials as they believe that this improves the quality of their research and of research in general. Also, they share because they want to support their fellow researchers. The most commonly stated reasons for not sharing research materials are the proprietary nature of the data used (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%). The reasons differ across methods. For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).

Collectively, our evidence speaks to the ongoing debate about reproducibility and openness of accounting research. We extend the survey evidence by @HLL_2020 by providing more detailed and current insights on the perceived benefits and costs of open science methods and by benchmarking the attitudes of the fields with neighboring disciplines. Also, we collaborate recent evidence on the robustness of empirical accounting [@G_2023; @S_2023; @LSA_2024; @CGL_2024] and management science [@FGHKO_2023] work by exploring some of the underlying reasons why our discipline might (or might not) have a reproducibility issue.

Our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work and the ability of research material sharing and pre-registration to improve it. This is consistent with these tools currently being less established in the accounting domain than in other fields. The challenges that hinder reproducibility and the potential effectiveness of open science methods vary across methodological paradigms. Qualitative research faces challenges different from archival quantitative work, and they both differ again from experimental studies. We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.

@@

Accounting is a field within the social sciences. As such, many of the arguments that have been developed with regard to the costs and benefits of open science in general [@MS_2019; @AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023] also apply to the field of accounting. In the following, we present and extend some of these thoughts in a voluntary disclosure framework [@LT_2005; @MS_2019; @BCLW_2010]. For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration. Understood as a disclosure activity related to underlying research, publicly available research materials constitute a public good. To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and, most likely, also the quality of research. Even if they are not really reusable or reusing them would be prohibitively costly, they still reduce the costs of reproducing the original work, thereby reducing assurance costs. As the work in auditing [e.g., @S_1980] posits, reduced auditing costs (easier reproduction) should lead to an overall increase in audit quality (more and better reproductions), resulting in better financial reporting quality (better research).

This means that, similar to other disclosure activities, sharing research materials does not necessarily benefit the producer but the research community at large. While intrinsic motivation for good research can be expected to be a strong determinant of individuals self-selecting into the academic accounting profession, one can still expect accounting researchers to under-engage in research material sharing because the production costs are mostly private while the benefits are mostly public. So, are there any private benefits to sharing research materials? Besides the warm glow of helping others, research material sharing likely improves the quality of the sharing individual's research output. First, it increases the likelihood that mistakes, conditionally on being present, are being detected. As it seems safe to assume that such incidents impose a cost on sharing researchers, this should increase their incentives to increase research quality prior to sharing. Second, if research materials are shared relatively early, the sharing researcher can directly benefit from community feedback prior to the ultimate publication of the study. Finally, uncovered mistakes are an important learning opportunity, likely improving research quality in the long run.

Based on these arguments, there are reasons to believe that voluntary research material sharing can act as a signal for research quality, creating an incentive for researchers to use it to signal the quality of their work in the publishing and career process. In ideal circumstances, we should obtain the well-known unraveling result where researchers even share and improve low-quality research because the research community would otherwise assume the worst [@M_1981]. One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the contemporary disclosure literature. Thus, for research materials sharing to be viable, it is important that the costs of sharing are sufficiently low, especially for researchers that produce high-quality work. Thus, it critically hinges on the above quality assurance process. Also, it depends on the direct and indirect costs of research material sharing to be bearable and at least comparable for high- and low-quality researchers.

The direct costs of research material sharing can be sizable. Preparing data, code and research procedures for dissemination requires time. While this time can also be expected to have a quality improvement effect (see above), at least some of the documentation work and code refactoring to increase accessibility and reusability creates costs that will not directly pay off on the quality of the underlying work. Another important factor to consider is the cost of maintaining publicly available materials. While some replication packages or similar materials are static in nature and require only limited maintenance, data and code packages can require ongoing updating and support activities. One important aspect of maintenance costs is that they increase significantly with public demand. As demand is directly linked to the scientific impact of the underlying work it can be argued that high maintenance cost sharing activities are likely to also be high benefit activities.

@@

Rational researchers can be expected to voluntarily share research materials when their private benefits outweigh their private costs. Whether this happens will critically depend on whether the signaling mechanism outlined above unfolds. In a credence good market like research, signaling is a key mechanism to avoid market failure. Based on the discussion above, a critical aspect could be the proprietary cost of competition, as one could argue that this cost is higher for high quality researchers with innovative ideas than for low-quality researchers who will likely face limited demand for their materials. Also the risks of reputation costs or misuse of materials could be higher for high-quality researchers. On the other hand, it can be argued that direct costs should be lower for high-quality researchers because of superior skills. Finally, outside options should be generally higher for high-quality researchers, meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their materials private.

The discussion should sound somewhat familiar to those who study voluntary disclosures by firms. What is different from our traditional firm-setting is that most researchers are not acting as entrepreneurs. Instead, they are employed by academic institutions or act as civil servants. This can, to some extent, mute the relevance of the benefits and the costs outlined above, at least for researchers with tenured positions. In addition, the employing institutions might also interact with the decision of whether or not to make research materials available. They are designing performance and tenure evaluation criteria that incentivize researchers. Also, they compensate researchers for their time and they provide them with infrastructure that influences and at times drastically reduces the direct costs of research material sharing. They might even hold property rights on the intellectual capital that their employees generate. Based on the public announcements of many leading academic institutions, it seems as if these are generally advocating the positive externalities of research material sharing. However, the incentive systems designed by these institutions appear at least in parts inconsistent with these announcements, as they value individual research achievements in form of publications and only rarely publicly available research materials.

Finally, publishers and journals are influential in research material sharing decisions as well. Leading journals have established demanding data and code sharing guidelines, essentially transforming the voluntary disclosure decision into a mandatory disclosure requirement. While journals also compete for the best papers and it is interesting to question how this competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.

@@

After eliciting respondents' perceptions on reproducibility, a set of questions explores their familiarity and experience with the practice of pre-registration. Lastly, we ask them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research. The survey ends with a few demographic questions. For a complete overview of the survey questions included in our study, please see Appendix A. All answers can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard} and the data is available in our public \href{https://github.com/joachim-gassen/osacc/}{GitHub repository} .

@@

Table 2 displays response demographics and characteristics based on a sample of up to 229 observations. Panel A reveals that the majority of the respondents are male, 35 years or older (87.8%), specializing in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%). Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we can collect about our population, we can only directly compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance. However, it seems likely that the study's all-European author team might have positively influenced the European response. While we control for geographical effects in our response (not-tabulated but available using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.

@@

The first research question of our study is to explore how accounting researchers perceive the reproducibility of influential findings in their field. Table 3 provides a comprehensive overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers with those of researchers in other disciplines, as recorded by @FLCPSWMBP_2023, based on their question, "How confident are you that the influential research findings in \[discipline\] would replicate?" Notably, we adapted the wording in this question from "replicate" to "reproduce" to ensure clarity for our audience, recognizing the nuanced distinctions between these terms across various research methodologies. The term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2020]. It implies the ability to recreate the results of prior studies using the same materials, procedures, and data as were used by the original researchers [@NSF_2015]. In contrast, the term "replication" has different interpretations for different fields. For instance, for experimental researchers, it refers to a distinct activity than reproduction (i.e., repeating an experimental study with new participants), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same or similar data using the same procedures). In turn, the definition that @FLCPSWMBP_2023 use for replication ("test of whether new studies on the same topic in a broadly similar sample support the same results.") seems relatively close to what we believe the common understanding of reproduction is in the area of accounting is. If anything, our notion of reproduction seems less demanding than the replication definition by @FLCPSWMBP_2023.

@@

The results in Table 3 reveal that accounting researchers generally hold a more critical view of the reproducibility of our influential findings. Compared to their peers in economics and sociology, accounting researchers exhibit a greater degree of doubt about the reproducibility of their influential work, with a difference of about half a point on a 5-point Likert scale. This difference is less stark when we compare accounting researchers to researchers in the fields of Political Science and Psychology. In a field fixed effect regression, in which we use Accounting as the baseline, we find that all four fixed field effects are statistically different from zero (two-tailed p-value \< 0.01). This skepticism is consistent with us accountants being more concerned about research quality, hinting at the existence of a credence-good problem that open science methods are designed to address.

@@

To delve deeper, we examine the assessments of reproducibility across different methodologies within Accounting. Accounting is not only a diverse discipline in terms of orientation and topic but also in terms of the methodologies its researchers employ. We distinguish among five categories: Analytical, Archival/Field, Experimental, Qualitative, and Survey. We asked respondents which of those categories best described their main methodological area, enabling us to categorize them in the data. Table 4 presents their assessments regarding the reproducibility of influential findings across three panels. Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B focuses on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.

@@

Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field relative to neighboring fields. Given this skepticism and following our discussion in section 2, one might expect accounting researchers to take a proactive stance on open science approaches, particularly regarding the sharing of research materials. Following the old proverb by Supreme Court Justice Luis Brandeis "sunlight is the best disinfectant," one would expect accountants to support increased transparency in research. The survey assesses this argument by asking respondents two questions about the practice of sharing research materials, which we define as the practice of sharing data, code, and research procedures. These two questions are also close adaptions of the survey done by @FLCPSWMBP_2023.

@@

To visualize the differences between these three questions, Figure 5 displays scatter box plots, one for each question and separately for each methodology. First, examining the three plots for the sample as a whole, a clear visual pattern emerges that the assessments of actual sharing behavior among accounting researchers lag behind assessments of whether accounting researchers favor sharing, which, in turn, lags behind assessments of whether editors value sharing. This pattern seems starker for respondents in the Archival/Field category. These findings suggest a contrast between the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior. In other words: We believe that we should share, and we also state that we do, but we do not believe that others do.

@@

Our survey has so far revealed that accounting researchers who participated in our survey are more skeptical about reproducibility than other social science areas. We also find that they are less familiar with research materials sharing as an open science practice that helps address reproducibility and that they find that practice less important. Besides research material sharing, our survey also covers a second Open Science practice: Pre-registration.[^6]

@@

Table 8 summarizes three questions about pre-registration. Panel A considers respondents' familiarity with the practice itself. We asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^7] The results in Panel A suggest that accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology. They seem to be slightly more familiar than researchers in Economics and Sociology (two-tailed p-value \< 0.010). While this finding might appear surprising at first glance, one has to factor in that the practice of pre-registration is gaining traction over time, and our survey was fielded two years later than the second wave of our benchmark survey.
